% Adjust these for the path of the theme and its graphics, relative to this file
%\usepackage{beamerthemeFalmouthGamesAcademy}
\usepackage{../../beamerthemeFalmouthGamesAcademy}
\usepackage{multimedia}
\graphicspath{ {../../} }

% Default language for code listings
\lstset{language=C++,
        morekeywords={each,in,nullptr}
}

% For strikethrough effect
\usepackage[normalem]{ulem}
\usepackage{wasysym}

\usepackage{pdfpages}

% http://www.texample.net/tikz/examples/state-machine/
\usetikzlibrary{arrows,automata}

\input{sessioninfo}

\begin{document}
\title{\sessionnumber: Unified Modelling Language}
\subtitle{\modulecode: \moduletitle}

\frame{\titlepage} 

\begin{frame}
	\frametitle{Learning Outcomes}
	\begin{itemize}
		\item \textbf{Illustrate} software architecture using UML
		\item \textbf{Assess}, at a basic level, the effectiveness of object interaction using a UML diagram
		\item \textbf{Apply} knowledge of UML to \textbf{describe} game architecture
	\end{itemize}
\end{frame}

\part{Workshop --- UML}
\frame{\partpage}

\begin{frame}{Unified Modelling Language}

	Review the UML Diagrams on the Agile Modeling website. \\
	
	(10 minutes) \\
	
	\vspace{1em}
	
	Then, complete the three worksheets:

	\begin{itemize}
		\item  UML1: Use-case and Class Diagrams
		\item  UML2: Activity and State Diagrams
		\item  UML3: Sequence and Interaction Diagrams
	\end{itemize}

	Each worksheet should take no longer than 40 minutes. \\
	
	\vspace{1em}
	
	Permit at least 5 minutes for your tutor to review your work.

\end{frame}

\part{Projects}
\frame{\partpage}

\begin{frame}{Research Essay}

	\begin{itemize}
		\item  There is no session in Week 4 --- you are to focus on your 200-word research essay proposal.
		\item  Make a pull-request by 5pm on Tuesday 14th February.
		\item  The themes your essay may focus upon include:
		\begin{itemize}
			\item  Engineering Software for Accessibility
			\item  Engineering Software for Portability
			\item  Engineering Software for Localisation
			\item  Incorporating Specialist Algorithms and Systems into Software
		\end{itemize}
		\item  You will need to coordinate your selection with your team, as each team member must focus on a different theme.
	\end{itemize}

\end{frame}

\begin{frame}{Unreal Projects}

	\begin{itemize}
		\item  You \textbf{must} attend product owner meetings. Not only are they \textbf{compulsory}, they are also \textbf{mark bearing}.
		\item  You need to evidence your individual contributions for COMP130/GAM130. Product owners are tracking this.
		\item  You need to prioritise the user stories and components to maximise your contributions. You cannot spend weeks making things that are not being used. You must deliver something every single sprint.
		\item  You \textbf{must} engage with and communicate with your team \textbf{on a daily basis}. Even if you can't make the daily stand-up meeting because of classes, you are still expected to check in with your team.
	\end{itemize}
	
\end{frame}

\end{document}
