% Adjust these for the path of the theme and its graphics, relative to this file
%\usepackage{beamerthemeFalmouthGamesAcademy}
\usepackage{../../beamerthemeFalmouthGamesAcademy}
\usepackage{multimedia}
\graphicspath{ {../../} }

% Default language for code listings
\lstset{language=C++,
        morekeywords={each,in,nullptr}
}

% For strikethrough effect
\usepackage[normalem]{ulem}
\usepackage{wasysym}

\usepackage{pdfpages}

% http://www.texample.net/tikz/examples/state-machine/
\usetikzlibrary{arrows,automata}

\input{sessioninfo}

\begin{document}
\title{\sessionnumber: Markets and Business Cases}
\subtitle{\modulecode: \moduletitle}

\frame{\titlepage} 

\begin{frame}
	\frametitle{Essential Resources}
	\begin{itemize}
		\item Hague \& Hague, 2004. Market Research in Practice. MRS.
		\item Osterwalder \& Pigneur, 2010. Business Model Generation: A Handbook for Visionaries, Game Changers, and Challengers. John Wiley and Sons.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Learning Outcomes}
	\begin{itemize}
		\item \textbf{Explain why} market evaluation is important
		\item \textbf{Explain how} to conduct a market evaluation
		\item \textbf{Analyse} the \textbf{key} points of consideration involved in market evaluations and business cases in games industry contexts
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Value of Market Evaluation}
	
	\textbf{Engage} in \textbf{dialogue} with your peers on the importance of evaluating markets \\
	(40 minutes)
	
	\vspace{2em}
	
	\textbf{Write} up notes on key points from the dialogue \\
	(5 minutes)
\end{frame}

\begin{frame}
	\frametitle{How To Evaluate Markets}
	
	\textbf{Engage} in \textbf{dialogue} with your peers on \textit{how} to evaluate markets \\
	(15 minutes)
	
	\vspace{2em}
	
	\textbf{Write} up notes on key points from the dialogue \\
	(5 minutes)
\end{frame}

\begin{frame}
	\frametitle{Case Study: PCG Tools}
	
	\textbf{Engage} in \textbf{dialogue} with your peers on the potential markets and business cases for procedural content generation and related tools \\
	(20 minutes)
	
	\vspace{2em}
	
	\textbf{Write} up notes on key points from the dialogue \\
	(5 minutes)
\end{frame}

\begin{frame}
	\frametitle{Case Study: Virtual Reality}
	
	\textbf{Engage} in \textbf{dialogue} with your peers on the potential markets and business cases for virtual reality technologies \\
	(40 minutes)
	
	\vspace{2em}
	
	\textbf{Write} up notes on key points from the dialogue \\
	(5 minutes)
\end{frame}

\begin{frame}
	\frametitle{Essential Practice}
	
	Please review this week's essential practice tasks on the LearningSpace. These are \textit{mandatory} and should be completed this week.
	
\end{frame}

\end{document}
