% Adjust these for the path of the theme and its graphics, relative to this file
%\usepackage{beamerthemeFalmouthGamesAcademy}
\usepackage[T1]{fontenc}
\usepackage{../../beamerthemeFalmouthGamesAcademy}
\usepackage{multimedia}
\graphicspath{ {../../} }

% Default language for code listings
\lstset{language=C++,
        morekeywords={each,in,nullptr}
}

% For strikethrough effect
\usepackage[normalem]{ulem}
\usepackage{wasysym}

\usepackage{pdfpages}

% http://www.texample.net/tikz/examples/state-machine/
\usetikzlibrary{arrows,automata}

\input{sessioninfo}

\begin{document}
\title{\sessionnumber: Personal Tutoring Year 2}
\subtitle{\modulecode: \moduletitle}

\frame{\titlepage} 

\begin{frame}
	\frametitle{Register}
	
	We are legally required to visually confirm your physical presence.
	
\end{frame}

\begin{frame}
	\frametitle{Learning Outcomes}
	\begin{itemize}
		\item \textbf{Identify} your personal tutor
		\item \textbf{Explain} the role of the personal tutor
		\item \textbf{Recall where} to look for support
		\item \textbf{Explain how} to book meetings with your personal tutor
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Who Is Your Personal Tutor?}
	\begin{center}
		Dr. Edward Powley
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Role of the Personal Tutor}	
	
	Your personal tutor is your:
	
	\begin{itemize}
		\item Your point of contact for any non-academic issue \textbf{or} any issue that is affecting your studies
		\item Your signpost to Falmouth University and FXU Services
		\item Your referee when you are looking for references
		\item Advice on continuing personal development
		\item Your champion for extra-curricular and enterprise opportunities 
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Role of the Personal Tutor}	
	
	\begin{center}
		Check-in with us regularly!
		\\~\\
		Let us know how things are going!
		\\~\\
		At least two meetings per study block
		\\~\\
		(Today counts as one meeting --- please book a second, 1-1 meeting via LearningSpace)
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Role of the Personal Tutor}	
	
	Please:
	
	\begin{itemize}
		\item There is no such thing as a minor or silly issue
		\item Do not wait for problems to get worse - we can help you to resolve them while they are small
		\item Trust your tutor - let them know about any challenges you encounter
		         \textbf{before} submitting a claim for extenuating circumstances
		\item Inform your tutor about any accessibility issues
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Attendance Monitoring}	
	
	Please:
	
	\begin{itemize}
		\item Your presence is monitored and you are expected to sign registers on the LearningSpace
		\item Failing to attend sessions will result in letters being sent to your term-time and home address
		\item You will need to justify your absence to your personal tutor
		\item Multiple absences cases will lead to the \textit{Student in Jeopardy} process
		\item Failing to engage with staff during this process will result in expulsion and freeze of funding
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Contacting Your Personal Tutor?}	
	
	\begin{itemize}
		\item Email: edward.powley@falmouth.ac.uk
		\item Slack: @edpowley
		\item \textbf{Not} Facebook!
		\item \textbf{Not} by phone!
		\item In person if it's urgent and/or quick --- otherwise better to email / Slack / book a meeting
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Personal Tutor Meetings}	
	\begin{itemize}
		\item You are expected to meet your tutor at least twice to check-in
		\item The two check-ins per study block are \textbf{mandatory}
		\item Book these meetings in advance on the LearningSpace
		
		\item Tutors have specified office hours, which differ based on their commitments
		\item We do not have enough time to see everyone every week! 
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Office Hours: Dr Edward Powley}	
	\begin{itemize}
		\item Wednesday 10am --- 12pm (during Programmers' Guild)
		\\~\\
		\item These may vary from week to week --- check LearningSpace
		\\~\\
		\item Please note that if there are no concerns to raise, we can instead do a CPD session.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{How Do I Book, Exactly?}	
	\begin{center}
		Live Demonstration (5 minutes)
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{What About Academic Support?}	
	\begin{enumerate}
		\item Review the resources on LearningSpace
		\item Leave a message in the relevant Slack channel
		\item Make a pull-request on GitHub
		\item Email the module leader
	\end{enumerate}
	
	We are a community, and we expect students to help each other.
\end{frame}

\begin{frame}
	\frametitle{And Everything Else...?}	
	\begin{itemize}
		\item Falmouth University --- \texttt{portal.falmouth.ac.uk}
		\item Student Union --- \texttt{www.fxu.org.uk}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Questions \& Answers}	
	\begin{center}
		Thank you for listening. 
		\\~\\
		Please feel welcome to ask questions or raise concerns.
	\end{center}
\end{frame}

\end{document}
