\part{Assignments}
\frame{\partpage}

\begin{frame}{COMP250 assignments}
	\begin{itemize}
		\pause\item \textbf{Two} assignments based on \textbf{one} portfolio project
		\pause\item Assignment 1: Computing Artefact (50\%)
		\pause\item Assignment 2: Technical Report (50\%)
		\pause\item These assignments assess the \textbf{architect} and \textbf{research} learning outcomes
	\end{itemize}
\end{frame}

\begin{frame}{The component task}
    \begin{itemize}
		\pause\item You will design and implement an \textbf{AI component}
		\pause\item Could be part of your GAM240 game, or a standalone demo project or tool
		\pause\item Must demonstrate an appropriately advanced AI technique
		\pause\item You are expected to do research beyond the topics covered in class
	\end{itemize}
\end{frame}

\begin{frame}{Deliverables}
    \begin{itemize}
		\pause\item Assignment 1: a 5-minute video demonstrating your component and describing its architecture
		\pause\item Assignment 2: a poster \textbf{and} a web page describing the architecture of the component,
			with appropriate references to research sources
	\end{itemize}
\end{frame}

\begin{frame}{Proposal}
    \begin{itemize}
		\pause\item For next week!
		\pause\item Prepare a 1-2 page proposal document covering the following:
		\begin{itemize}
			\pause\item What is the high concept of your computing artefact?
			\pause\item What functionality will your component include?
			\pause\item How does your component fit into your chosen specialism?
			\pause\item Why is this artefact needed?
			\pause\item What are the key requirements?
			\pause\item Is the scope appropriate for the product development time-frame?
			\pause\item How will you address the architect and research requirement?
		\end{itemize}
	\end{itemize}
\end{frame}
