\part{What is AI?}
\frame{\partpage}

\begin{frame}{What is AI?}
	\begin{itemize}
		\item Socrative FALCOMPED
		\item Discuss for \textbf{5 minutes}
		\item Suggest a \textbf{one sentence} definition of artificial intelligence (AI)
	\end{itemize}
\end{frame}

\begin{frame}{What is AI?}
    \begin{itemize}
        \pause\item[\xmark] Simulating human brains or human intelligence
        \pause\item[\cmark] Performing tasks by machine (or by software) which would ordinarily require human intelligence
        \pause\item[\cmark] Making decisions to achieve goals
    \end{itemize}
\end{frame}

\begin{frame}{What is AI?}
    \begin{itemize}
        \pause\item[\xmark] Programming machines to learn by themselves
        \pause\item[\cmark] Machine learning is an important sub-field of AI, but there are many other AI techniques
    \end{itemize}
\end{frame}

\begin{frame}{What is AI?}
    \begin{itemize}
        \pause\item[\xmark] Programming machines to possess general intelligence, self-awareness, consciousness
        \pause\item[\cmark] Maybe one day, but for now this is pure sci-fi
        \pause\item[\cmark] Programming machines to carry out (or learn to carry out) a specific type of task
    \end{itemize}
\end{frame}

\begin{frame}{Computers vs brains}
	Discuss:
	\begin{itemize}
		\pause\item For what kinds of tasks are digital computers ``better'' than human brains?
		\pause\item For what kinds of tasks are human brains ``better'' than digital computers?
		\pause\item For what kinds of tasks are both ``good'', but approach the task in different ways?
	\end{itemize}
\end{frame}

\begin{frame}{Is it AI?}
	Discuss: are these examples of AI?
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\begin{itemize}
				\pause\item Calculator
				\pause\item Computer opponent in a chess program
				\pause\item Enemy in a video game
				\pause\item Facebook newsfeed
				\pause\item Autocorrect in a text messaging app
				\pause\item Autocompletion in an IDE
				\pause\item Spellchecker
			\end{itemize}
		\end{column}
		\begin{column}{0.48\textwidth}
			\begin{itemize}
				\pause\item Satellite navigation
				\pause\item Virtual assistant (e.g.\ Siri, Alexa, Cortana etc.)
				\pause\item Amazon product recommendations
				\pause\item Search function in a text editor
				\pause\item Google search
				\pause\item C++ compiler
				\pause\item Robot
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

