\documentclass[a4paper]{article}

\usepackage{url}

\usepackage{listings}
\lstset{
    basicstyle=\ttfamily,
	frame=single,
	tabsize=4,
	showstringspaces=false,
	breaklines=true,
    language=C++
}

\title{SDL Project Setup}
\author{Ed Powley}

\begin{document}

\maketitle

\section{Creating the project}

\begin{enumerate}
    \item Open \textbf{Visual Studio Community 2015} and click \textbf{New Project}.
    \item Choose \textbf{Templates $\to$ Visual C++ $\to$ Win32 $\to$ Win32 Project} and click \textbf{OK}.
    \item Click \textbf{Finish}.
    \item Add the following line to \texttt{stdafx.h}:
    \begin{lstlisting}
#include <SDL.h>
    \end{lstlisting}
    \item Delete all the code in the main \texttt{.cpp} file except for the two \texttt{\#include} statements.
    \item Add the following code:
    \begin{lstlisting}
int main(int argc, char* args[])
{
	return 0;
}
    \end{lstlisting}
\end{enumerate}

\section{Downloading SDL}

\begin{enumerate}
    \item Go to \url{http://libsdl.org}, click on \textbf{Download SDL 2.0},
        and download the \textbf{Development Libraries} for \textbf{Visual C++ 32/64 bit}.
    \item Extract the downloaded zip to a convenient location, for example the folder for your new project.
\end{enumerate}

\section{Setting up the project}

\begin{enumerate}
    \item Right click your project in the Solution Explorer, and click \textbf{Properties}.
    \item Ensure the boxes at the top are set to \textbf{All Configurations} and \textbf{All Platforms}.
    \item Under \textbf{VC++ Directories}, click \textbf{Include Directories} and click \textbf{Edit}.
    \item Add the path to the \texttt{include} directory extracted from the SDL zip.
        \emph{Tip:} use relative paths rather than absolute, e.g.\ \verb!..\SDL2-2.0.4\include! instead of \verb!C:\Users\Ed\Documents\SDL2-2.0.4\include!.
    \item Change the \textbf{Platform} to \textbf{Win32}. Edit the \textbf{Library Directories} entry, adding the path to \verb!lib\x86!.
    \item Change the \textbf{Platform} to \textbf{x64}. Edit the \textbf{Library Directories} entry, adding the path to \verb!lib\x64!.
    \item Change the \textbf{Platform} back to \textbf{All Platforms}.
    \item Under \textbf{Linker $\to$ Input}, edit \textbf{Additional Dependencies} and add \texttt{SDL2.lib} and \texttt{SDL2main.lib}.
    \item Click \textbf{OK}.
\end{enumerate}

\section{Running the project}

\begin{enumerate}
    \item Build and run the project as normal. You should receive an error message saying SDL2.dll cannot be found.
    \item Find SDL2.dll in SDL's \verb!lib\x86! or \verb!lib\x64! directory (depending on which platform you are currently targeting).
    \item \textbf{Copy} SDL2.dll into your project's \verb!Debug!, \verb!Release!, \verb!x64\Debug! or \verb!x64\Release! directory
        (depending on which platform you are currently targeting).
    \item Run the project again.
\end{enumerate}

\section{What now?}

Write the code to make your game do something! Refer to the live coding examples from class, the SDL Game Development book, and online tutorials.

\end{document}
