% Adjust these for the path of the theme and its graphics, relative to this file
%\usepackage{beamerthemeFalmouthGamesAcademy}
\usepackage{../../beamerthemeFalmouthGamesAcademy}
\usepackage{multimedia}
\graphicspath{ {../../} }

\usepackage{textcomp}

% Default language for code listings
\lstset{language=Python, upquote=true,
        morekeywords={each,in,nullptr}
}

% For strikethrough effect
\usepackage[normalem]{ulem}
\usepackage{wasysym}

\usepackage{pdfpages}

% http://www.texample.net/tikz/examples/state-machine/
\usetikzlibrary{arrows,automata}

\input{sessioninfo}

\setbeamertemplate{navigation symbols}{}

\input{../../commands}

\begin{document}
\title{\sessionnumber: Computing Professionals}
\subtitle{\modulecode: \moduletitle}

\frame{\titlepage} 

\begin{frame}
	\frametitle{Learning Outcomes}
	\begin{itemize}
		\item \textbf{Analyse} the role of computing professionals in the games industry
		\item \textbf{Recall} important theories about learning computer programming
		\item \textbf{Apply} pair programming practices to solve simple problems
	\end{itemize}
\end{frame}

\part{Professional Roles}
\frame{\partpage}

\begin{frame}
	\frametitle{TwitterFall Activities}
		
	\begin{itemize}
		\item Self-organise into small groups of 3-4
		\item Load a Twitter app, or login to Twitter on a PC
		\item Conduct research on the given topic
		\item Post a tweet when you find something interesting
	\end{itemize}

	\begin{itemize}
		\item Please use the hashtag for the module (i.e., \lstinline{\#comp120})
		\item Also please ensure you use the @ symbol to open and continue discussions
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{TwitterFall Activity \#1}
	
	\textbf{Answer} the follow question:
	
	\vspace{1em}
	
	``What do computing professionals do, \textit{generally}?''
	
	\vspace{1em}
	
	You have:
	
	\begin{itemize}
		\item 10 minutes to conduct research and tweet to \lstinline{\#comp120}
		\item 5 minutes to debrief
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{TwitterFall Activity \#2}
	
	\textbf{Answer} the follow question:
	
	\vspace{1em}
	
	``What do computing professionals do, \textit{in games}?''
	
	\vspace{1em}
	
	You have:
	
	\begin{itemize}
		\item 10 minutes to conduct research and tweet to \lstinline{\#comp120}
		\item 5 minutes to debrief
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{TwitterFall Activity \#3}
	
	\textbf{Answer} the follow question:
	
	\vspace{1em}
	
	``What career options are available to graduates with B.Sc. degrees in computing?''
	
	\vspace{1em}
	
	You have:
	
	\begin{itemize}
		\item 10 minutes to conduct research and tweet to \lstinline{\#comp120}
		\item 5 minutes to debrief
	\end{itemize}
\end{frame}

\part{Professional Development}
\frame{\partpage}

\begin{frame}
	\frametitle{Continuing Professional Development}
	
	\begin{itemize}
		\item Games industry is fast-moving
		\item Learning does not end at school and university
		\item A goal of this course is to facilitate your development as self-regulated learners
		\item Gradually, more independence across each year of study
		\item This is a science degree, which means you will become a producer of knowledge, not just a consumer of knowledge!
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Continuing Professional Development}
	
	\begin{itemize}
		\item It isn't easy!
		\item Many of you will encounter programming anxiety
		\item Some will experience a sense of fear or a sense of hopelessness --- it is more common than you think
		\item Some will need more support than others --- this isn't a bad thing
		\item Everyone who puts in the time and effort will eventually achieve mastery
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Key Learning Theories}
	
	\begin{itemize}
		\item Deliberate Practice
		\item Scaffolding and the Zone of Proximal Development
		\item Schema Development
		\item Cognitive Load
		\item Learning Edge Momentum
		\item Mindset
		\item Neuroplasticity
		\item Self-Determination
	\end{itemize}
\end{frame}

\fullbleed{deliberate_practice}

\begin{frame}
	\frametitle{Deliberate Practice}
	
	``\textbf{Attention to the task:} It is essential to pay fixed attention. The more a student's
	mind wanders, the less the rate of change. Even videogames require the subject to stay
	`locked in' to the content and the process.''
	
	 (Jensen, 2006, p. 82) 
	
\end{frame}

\begin{frame}
	\frametitle{Deliberate Practice}
	
	``\textbf{Low to moderate stress:} This variable is quite slippery because what is stressful
	for one may not be stressful for another. The bottom line is that the subject must perceive
	some choice or control over the task and the surrounding conditions. Otherwise, the stress 
	from that loss of control may neutralize the positive effects from the learning.''
	
	 (Jensen, 2006, p. 82) 
	
\end{frame}

\fullbleed{performance-pressure}

\fullbleed{zpd}

\fullbleed{schema_theory}

\fullbleed{cognitive_load}

\fullbleed{network_lem}

\begin{frame}
	\frametitle{Mindsets}
	
	Watch the video at:
	
	\vspace{1.5em}
		
	\url{https://www.dropbox.com/s/8wy1mbkud7n5ns3/Growth\%20vs\%20Fixed\%20Mindset.mp4?dl=0}
	
	\vspace{1em}
		
	(5 minutes)
	
\end{frame}

\fullbleed{mj_growth_mindset}

\begin{frame}
	\frametitle{Neuroplasticity}
	
	Medina (2008) demonstrates:
	
	\begin{itemize}
		\item \textbf{Neuroplasticity}: the ability of the brain to reorganise itself and 
		create new circuits in response to our environment and, perhaps most remarkably,
		 in response to our thoughts
		\item \textbf{Life-long plasticity}: scientists discovered decades ago that the human
		brain remains plastic throughout our lives
		\item \textbf{New Nuron Growth}: more recent research shows that stem cells in the brain
		can grow new neurons at any age (i.e., Gage, 2002).
		\item \textbf{Epigenetics}: no such thing as a `geek gene', considerable
		variance in \textit{gene expression}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Neuroplasticity}
	
	Medina's (2008) also notes the following `brain rules':
	
	\begin{itemize}
		\item Exercise: Physical health matters.
		\item Survival: Human brain evolves, too.
		\item Wiring: Every brain is wired differently.
		\item Attention: The brain won't pay attention to boring things.
		\item Short-term Memory: Repeat to remember.
		\item Long-term Memory: Remember to repeat.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Neuroplasticity}
	
	Medina's (2008) also notes the following `brain rules':
	
	\begin{itemize}
		\item Sleep: sleep well, think well.
		\item Stress: anxiety impairs learning.
		\item Sensory Integration: Try to stimulate all of your senses.
		\item Vision: vision trumps the other senses.
		\item Exploration: humans are natural explorers, nurture this.
	\end{itemize}
\end{frame}

\fullbleed{sdt}

\part{Professional Practice}
\frame{\partpage}

\begin{frame}
	\frametitle{Pair Programming}
		
	Pair programming is an agile software development technique in which two programmers work together 
	at one workstation. 
	\\~\\
	One, the driver, writes code while the other, the observer or navigator, reviews 
	each line of code as it is typed in. 
	\\~\\
	The two programmers switch roles frequently.
	
\end{frame}

\begin{frame}
	\frametitle{Pair Programming}
	
	Watch the video at:
	
	\vspace{1.5em}
		
	\url{https://www.youtube.com/watch?v=ET3Q6zNK3Io}
	
	\vspace{1em}
		
	(5 minutes)
	
\end{frame}

\begin{frame}
	\frametitle{Pair Programming}
	
	Review the guidelines at:
	
	\vspace{1.5em}
		
	\url{http://www.pairprogramming.co.uk/}
	
	\vspace{1em}
		
	(10 minutes)
	
\end{frame}

\begin{frame}
	\frametitle{Pair Programming}
	
	Watch the video at:
	
	\vspace{1.5em}
		
	\url{https://www.youtube.com/watch?v=ONnYCT_LJio}
	
	\vspace{1em}
		
	(5 minutes)
	
\end{frame}

\begin{frame}
	\frametitle{Pair Programming Challenge}
	
	\begin{itemize}
		\item In pairs
		\item \textbf{Implement} the code excerpt
		\item \textbf{Fix} the errors in the code excerpt
		\item \textbf{Modify} the code excerpt to incorporate functions and arguments
		\item \textbf{Post} your solution to the \lstinline{\#comp120} slack channel
	\end{itemize}
	
	You can learn more about functions and arguments at:
	
	\vspace{1em}
	
	 \url{https://docs.python.org/3/tutorial/controlflow.html\#defining-functions}
	
	\vspace{1em}
	
	(20 minutes)
	
\end{frame}

\begin{frame}[fragile]
	\frametitle{Pair Programming Challenge}
	
	The function:

	\begin{lstlisting}
		def madlib()
	\end{lstlisting}
	
	\vspace{1.5em}
	
	Should become:
	
	\begin{lstlisting}
		def madlib(name, pet, verb, snack)
	\end{lstlisting}
	
\end{frame}

\begin{frame}[fragile]
	\frametitle{Pair Programming Challenge}
	
	\begin{lstlisting}
def madlib():
	name = 'Mike'
	pet = 'Spyro'
	verb = 'ate'
	snack = 'doughnuts'
	line1 = 'once upon a time,' + name + ' walked'
	line2 = ' with ' + pet + ', a trained dragon.'
	line3 = 'Suddenly, ' + pet + ' announced,'
	line4 = 'I really want some ' + snack + '!'
	line5 = name + ' complained. Where am I going to get that?'
	line6 = 'Then ' + name + 'found a wizard's wand.'
	line 7 = 'With a wave of the wand, '
	line8 = pet + ' got ' + snack + '. '
	line9 = 'Perhaps surprisingly, ' + pet + ' ' + verb + '  ' + snack
	print line1 + line2 + line3 + line4
	print line5 + line6 + line7 + line8 + line9

\end{lstlisting}
	
\end{frame}

\end{document}