% Adjust these for the path of the theme and its graphics, relative to this file
%\usepackage{beamerthemeFalmouthGamesAcademy}
\usepackage[T1]{fontenc}
\usepackage{../../beamerthemeFalmouthGamesAcademy}
\usepackage{multimedia}
\graphicspath{ {../../} }

% Default language for code listings
\lstset{language=C++,
        morekeywords={each,in,nullptr}
}

% For strikethrough effect
\usepackage[normalem]{ulem}
\usepackage{wasysym}

\usepackage{pdfpages}

% http://www.texample.net/tikz/examples/state-machine/
\usetikzlibrary{arrows,automata}

\input{sessioninfo}

\begin{document}
\title{\sessionnumber: Personal Tutoring}
\subtitle{\modulecode: \moduletitle}

\frame{\titlepage} 

\begin{frame}
	\frametitle{Activity}
	
	Raise your hand when you see your first games console:  \pause
	
	\begin{itemize}
		\item Magnavox Odyssey \pause
		\item Atari 2600 \pause
		\item BBC Micro \pause
		\item Vectrex \pause
		\item Nintendo Entertainment System \pause
		\item Sega Master System \pause
		\item Sega Mega Drive \pause
		\item Nintendo GameBoy \pause
		\item Super Nintendo Entertainment System

	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Activity}
	
	Raise your hand when you see your first games console:
	
	\begin{itemize}
		\item Sony PlayStation \pause
		\item Nintendo 64 \pause
		\item Nintendo GameBoy Color \pause
		\item Sega Dreamcast \pause
		\item Sony PlayStation 2 \pause
		\item Nintendo GameCube \pause
		\item Microsoft Xbox \pause
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Activity}
	
	Raise your hand when you see your first games console:
	
	\begin{itemize}
		\item Microsoft Xbox 360 
		\item Sony PlayStation 3  \pause
		\item Nintendo Wii  \pause
		\item Nintendo Wi U  \pause
		\item Sony PlayStation 4 \pause
		\item Microsoft Xbox One \pause
		\item Nintendo Switch \pause
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Attendance Monitoring}
	
	We are (legally) required to confirm your physical presence. Please remember to swipe-into all of your timetabled sessions.
	
\end{frame}

\begin{frame}
	\frametitle{Learning Outcomes}
	\begin{itemize}
		\item \textbf{Identify} your personal tutor
		\item \textbf{Explain} the role of the personal tutor
		\item \textbf{Recall where} to look for support
		\item \textbf{Explain how} to book meetings with your personal tutor
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Who Is Your Personal Tutor?}

	I am!

	\begin{itemize}
		\item Office Hours
		\item Booking on LearningSpace
		\\~\\
		\item You need to see me \textit{twice} per study block, even if everything is okay --- today counts as the first meeting.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Role of the Personal Tutor}	
	
	Your personal tutor is your:
	
	\begin{itemize}
		\item Your point of contact for any non-academic issue \textbf{or} any issue that is affecting your studies
		\item Your signpost to Falmouth University and FXU Services
		\item Your referee when you are looking for references
		\item Advice on continuing personal development
		\item Your champion for extra-curricular and enterprise opportunities 
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Role of the Personal Tutor}	
	
	\begin{center}
		Check-in with us regularly!
		\\~\\
		Let us know how things are going!
		\\~\\
		We can direct you to support services.
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Role of the Personal Tutor}	
	
	Please:
	
	\begin{itemize}
		\item There is no such thing as a minor or silly issue
		\item Do not wait for problems to get worse - we can help you to resolve them while they are small
		\item Trust your tutor - let them know about any challenges you encounter
		         \textbf{before} submitting a claim for extenuating circumstances
		\item Inform your tutor about any accessibility issues
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Attendance Monitoring}	
	
	Please:
	
	\begin{itemize}
		\item Your presence is monitored and you are expected to sign registers on the LearningSpace
		\item Failing to attend sessions will result in letters being sent to your term-time and home address
		\item You will need to justify your absence to your personal tutor
		\item Multiple absences cases will lead to the \textit{Student in Jeopardy} process
		\item Failing to engage with staff during this process will result in expulsion and freeze of funding
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Contacting Your Personal Tutor?}	
	
	You can contact us:
	
	\begin{itemize}
		\item Via Email
		\\~\\
		or
		\\~\\
		\item Via Telephone
		\\~\\
		\item (Some tutors are okay with other methods)
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{How Do You Contact Your Personal Tutor?}
	
	Please contact module leaders and subject specialists regarding academic issues. Slack is great for this. So are supervised studio hours. Please contact technicians for technical problems and access to kit. They are based in our studios.	

\end{frame}

\begin{frame}
	\frametitle{How Do You Contact Your Personal Tutor?}	
	\begin{itemize}
		\item Please \textbf{do not} use social media like Facebook
		\item Most tutors do not receive any notifications from social media like Facebook
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{How Do You Contact Your Personal Tutor?}
	
	Please note:
				
	\begin{itemize}
		\item Academics are seldom at their desks --- book ahead on LearningSpace
		\item Falmouth University does \textbf{not} recognise a telephone call as a point of contact because there is no record of it
		\item Do not call tutors after 5pm, use \texttt{https://www.fxplus.ac.uk/students/student-services/need-help-now}		
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Personal Tutor Meetings}	
	\begin{itemize}
		\item You are expected to meet your tutor at least twice to check-in
		\item The two check-ins per study block are \textbf{mandatory}
		\item Book these meetings in advance on the LearningSpace
		
		\item Tutors have specified office hours, which differ based on their commitments
		\item We do not have enough time to see everyone every week! 
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{How Do I Book, Exactly?}	
	\begin{center}
		Live Demonstration (5 minutes)
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Your First Tutor Meeting}	
	
	We will check that you have:
	
	\begin{itemize}
	\item Collected your Student ID card
	\item Enrolled on the right course
	\item Completed All Enrolment Activities at myfalmouth.falmouth.ac.uk
	\item Know how to access to your Personal Timetable
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Your First Tutor Meeting}	
	
	We will check that you have:
	
	\begin{itemize}
	\item Know how to access to your Personal Email Account
	\item Access to the Games Academy Courses Page on LearningSpace
	\item Access to the Relevant Modules on LearningSpace
	\item Aware of the Facebook Group
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Your First Tutor Meeting}	
	
	We will check that you have:
	
	\begin{itemize}
	\item Successfully Logged Into a Lab Computer
	\item Registered on FXU and Nominated a Student Rep
	\item Familiarised yourself with the course requirements
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Your First Tutor Meeting}	
	
	If you're in computing, we will check that you have:
	
	\begin{itemize}
	\item Joined the Slack Group
	\item Joined the Falmouth Games Academy GitHUB Team
	\item Accessed the Socrative App
	\end{itemize}
\end{frame}


\begin{frame}
	\frametitle{What About Academic Support?}	
	\begin{enumerate}
		\item Review the resources on LearningSpace
		\item Leave a message in the relevant Slack channel
		\item Make a pull-request on GitHub
		\item Email the module leader
	\end{enumerate}
	
	We are a community, and we expect students to help each other.
\end{frame}

\begin{frame}
	\frametitle{And Everything Else...?}	
	\begin{itemize}
		\item Falmouth University --- \texttt{portal.falmouth.ac.uk}
		\item Student Union --- \texttt{https://www.fxu.org.uk/}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Any Advice?}	
	
	Time Management:
	
	\begin{itemize}
		\item Purchase a diary \textbf{or} setup a calendar app on your phone
		\item Buy a large calender \textbf{and} mount it on your wall, then label it with all of the assignment deadlines
		\item Setup a kanban-style task board on another wall, then use post-it notes as a to-do list
		\item Specify in advance what nights you will go out and stick to it (not the nights before a 9am lecture)
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Any Advice?}	
	
	\begin{itemize}
		\item All \textbf{summative} assignment deadlines are on \texttt{myfalmouth.falmouth.ac.uk}
		\\~\\
		\item All \textbf{formative} assignment deadlines are in the assignment briefs on \texttt{learningspace.falmouth.ac.uk}, and are clear in session titles
	\end{itemize}
\end{frame}


\begin{frame}
	\frametitle{Any Advice?}	
	
	Get A Head Start:
	
	\begin{itemize}
		\item Play SpaceChem
		\item It is available in the lab, but a copy on Steam is only \textsterling 7
		\\~\\
		\item Your first worksheet will be to complete several of the levels
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Any Advice?}	
	
	Update Your Email:
	
	\begin{itemize}
		\item Setup an auto-forward rule to redirect your university email to an account you actually use
		\\~\\
		\item It is really easy and it takes less than 5 minutes:
		\item \url{https://www.youtube.com/watch?v=otr6fmAXKxs}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Questions \& Answers}	
	\begin{center}
		Thank you for listening. 
		\\~\\
		Please feel welcome to ask questions or raise concerns.
	\end{center}
\end{frame}

\end{document}
