% Adjust these for the path of the theme and its graphics, relative to this file
%\usepackage{beamerthemeFalmouthGamesAcademy}
\usepackage{../../beamerthemeFalmouthGamesAcademy}
\usepackage{multimedia}
\graphicspath{ {../../} }

% Default language for code listings
\lstset{language=C++,
        morekeywords={each,in,nullptr}
}

% For strikethrough effect
\usepackage[normalem]{ulem}
\usepackage{wasysym}

\usepackage{pdfpages}

% http://www.texample.net/tikz/examples/state-machine/
\usetikzlibrary{arrows,automata}

\input{sessioninfo}

\begin{document}
\title{\sessionnumber: Design Patterns}
\subtitle{\modulecode: \moduletitle}

\frame{\titlepage} 

\begin{frame}{Learning Outcomes}
	Today's lecture will introduce the basics of object-orientated software design and design patterns, focusing on
	the following patterns:
	
	\vspace{2ex}
	
	\begin{columns}[onlytextwidth]
		\begin{column}{0.33\textwidth}
			\begin{itemize}
				\item Singleton
				\item Typesafe Enum
				\item Factory
				\item Prototype
				\item Builder
			\end{itemize}
		\end{column}
		\begin{column}{0.33\textwidth}
			\begin{itemize}
				\item Adapter
				\item Bridge
				\item Proxy
				\item Facade
				\item Decorator
			\end{itemize}
		\end{column}
		\begin{column}{0.33\textwidth}
			\begin{itemize}
				\item Template
				\item State
				\item Observer
				\item Visitor				
				\item Strategy
			\end{itemize}
		\end{column}
	\end{columns}
	
	\vspace{3ex}
	 
	There are many other design patterns that you will be able to discover through independent study.
	
\end{frame}

\begin{frame}{Further Reading}
	\begin{itemize}
		\item Alexander, C. (1977) \textit{A Pattern Language}. Oxford University Press.	
		\vspace{1ex}
		\item Alexander, C. (1979) \textit{The Timeless Way of Building}. Oxford University Press.
		\vspace{1ex}
		\item Coad, P. (1992) \textit{Object-orientated Patterns}.Communications of the ACM, vol. 35, no. 9, pp. 152---159.
	\end{itemize}
\end{frame}

\begin{frame}{Further Reading}
	\begin{itemize}
		\item Johnson, R.E. (1992) `Documenting frameworks using patterns'. In: \textit{Proceedings of the 1992 Conference on 
		Object-oriented Programming Systems, Languages, and Applications} (OOPSLA '92). ACM, New York, pp. 63-76.
		\vspace{1ex}
		\item Gamma, E., Helm, R., Johnson, R., and Vlissides, J. (1993) `Design Patterns: Abstraction and Reusage of
		Object-Orientated Design'. In: \textit{Proceedings of the 7th European Conference on Object-Orientated Programming}
		(ECOOP `93). Springer, New York, pp. 406-431.
	\end{itemize}
\end{frame}

\begin{frame}{Further Reading}
	\begin{itemize}
		\item Gamma, E., Helm, R., Johnson, R., and Vlissides, J. (1995). Design patterns: elements of reusable object-oriented software. Addison-Wesley.
		\vspace{2ex}
		\item Fowler, M. (2002) \textit{Patterns of enterprise application architecture}. Addison-Wesley.
	\end{itemize}
\end{frame}

\input{design_patterns}

\part{Practical Activity}
\frame{\partpage}

\begin{frame}{Design Patterns}
	\begin{itemize}
		\item \textbf{Self-organise} into your project teams.
		\item \textbf{Review} the design of your game's architecture.
		\item If you have not yet done so, \textbf{draw} a UML class diagram that illustrates the game's architecture.
		\item \textbf{Identify} existing patterns \textbf{and} opportunities to apply pattern.
		\item \textbf{Refactor} the design accordingly.
	\end{itemize}
	
	(45 minutes)
\end{frame}
		
\part{Projects}
\frame{\partpage}

\begin{frame}{Research Essay}

	\begin{itemize}
		\item  There is no session in Week 4 --- you are to focus on your 200-word research essay proposal.
		\item  Make a pull-request by 5pm on Tuesday 14th February.
		\item  The themes your essay may focus upon include:
		\begin{itemize}
			\item  Engineering Software for Accessibility
			\item  Engineering Software for Portability
			\item  Engineering Software for Localisation
			\item  Incorporating Specialist Algorithms and Systems into Software
		\end{itemize}
		\item  You will need to coordinate your selection with your team, as each team member must focus on a different theme.
	\end{itemize}

\end{frame}

\begin{frame}{Unreal Projects}

	\begin{itemize}
		\item  You \textbf{must} attend product owner meetings. Not only are they \textbf{compulsory}, they are also \textbf{mark bearing}.
		\item  You need to evidence your individual contributions for COMP130/GAM130. Product owners are tracking this.
		\item  You need to prioritise the user stories and components to maximise your contributions. You cannot spend weeks making things that are not being used. You must deliver something every single sprint.
		\item  You \textbf{must} engage with and communicate with your team \textbf{on a daily basis}. Even if you can't make the daily stand-up meeting because of classes, you are still expected to check in with your team.
	\end{itemize}

\end{frame}

\end{document}
